---
title: "Data Cleanup"
author: "Josephine Decker"
date: "2023-09-15"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
```



```{r}
DAWBA <- read_csv("DAWBA_database.csv")

#View(DAWBA)

```


#### Cleaning DAWBA 

##### Data with written responses (Youth)

1. got rid of any columns with a percentage of NA's greater than 60%. 
2. Looked at the sections with the greatest amount of questions left.
3. Decided to only include questions answered by the youth. Of the questions both answered by the youth and the parents, 79% of the time the parent rated them more likely in each section. 
4. Sections that are included in final data set : BDD, Depression, DMDD, Generalized Anxiety, OCD. 
5. Final data set has a 98 questions and 1 identifier variable. 
6. Re-coded the numeric data to have the written answers instead. 
```{r}
dim(DAWBA)

w_DAWBA <- DAWBA[, colMeans(is.na(DAWBA)) <= .60]  #getting rid of the columns with a percentage of NAs greater than 60%

dim(w_DAWBA) #checking the dimensions after cutting the previous columns.

w_DAWBA <- w_DAWBA[, -c(517:531)] #deleting the "other concerns" questions

w_DAWBA <- w_DAWBA[, -c(240:251)] #deleting the heights and weights

w_DAWBA <- w_DAWBA[, -c(2:56)] #deleting general + Prediction sections

dim(w_DAWBA) #checking dimensions after deletions of non necessary questions


#Deleting all the questions that are the youth answers of Depression, DMDD, Generalized Anxiety, OCD, BDD

w_DAWBA <- w_DAWBA[, -c(2:107, 136:143, 173:203, 221:239, 256:278, 289:449)]

w_DAWBA <- w_DAWBA[, -c(12)]
#view(w_DAWBA)

dim(w_DAWBA) #One identifier and 99 questions




# Re-coding the variables from numeric to written response ------- BDD Section
w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(2:18), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "a little",
    . == 2 ~ "a lot"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(19:20), ~ case_when(
    . == 0 ~ "little or no time",
    . == 1 ~ "less than an hour",
    . == 2 ~ "about an hour",
    . == 3 ~ "a few hours",
    . == 4 ~ "many hours" ))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(21:22), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "perhaps",
    . == 2 ~ "definitely"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(23:28), ~ case_when(
    . == 0 ~ "not at all",
    . == 1 ~ "a little",
    . == 2 ~ "a medium amount",
    . == 3 ~ "a great deal"))

# --------------------------------- Depression Section

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(29:31, 34:36, 39:41, 43:51), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "yes"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(32,37), ~ case_when(
    . == 0 ~ "easily",
    . == 1 ~ "with difficulty/only briefly",
    . == 2 ~ "not at all"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(33,38,42), ~ case_when(
    . == 0 ~ "less than 2 weeks",
    . == 1 ~ "2 weeks or more"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(52:57), ~ case_when(
    . == 0 ~ "not at all",
    . == 1 ~ "a little",
    . == 2 ~ "a medium amount",
    . == 3 ~ "a great deal"))

#------------------------------------ DMDD Section

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(58:59), ~ case_when(
    . == 0 ~ "never",
    . == 1 ~ "occasionally",
    . == 2 ~ "once or twice a week",
    . == 3 ~ "three or more times a week",
    . == 4 ~ "every day"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(60:61, 64:66, 68), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "a little",
    . == 2 ~ "a lot"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(62), ~ case_when(
    . == 0 ~ "no more than a few minutes",
    . == 1 ~ "less than an hour",
    . == 2 ~ "a few hours",
    . == 3 ~ "most or all of the day"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(63, 70:74), ~ case_when(
    . == 0 ~ "not at all",
    . == 1 ~ "a little",
    . == 2 ~ "a medium amount",
    . == 3 ~ "a great deal"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(67), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "yes"))

#--------------------------------- Generalized Anxiety Section

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(75:76, 89:90), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "yes"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(77), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "perhaps",
    . == 2 ~ "definitely"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(78:88), ~ case_when(
    . == 0 ~ "no more than others",
    . == 1 ~ "a little more than others",
    . == 2 ~ "a lot more than others"))

#----------------------------------- OCD Section

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(91), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "yes"))

w_DAWBA <- w_DAWBA %>%
  mutate_at(vars(92:100), ~ case_when(
    . == 0 ~ "no",
    . == 1 ~ "a little",
    . == 2 ~ "a lot"))

w_DAWBA <- w_DAWBA[, -c(69)]
view(w_DAWBA)



# saving the file
file_path <- "w_DAWBA.csv"
write.csv(w_DAWBA, file = file_path, row.names = FALSE)

```







##### Dataset utilizing the numeric data to explore data

```{r}
# colMeans(is.na(DAWBA)) > .60
```

```{r}
dim(DAWBA)

c_DAWBA <- DAWBA[, colMeans(is.na(DAWBA)) <= .60]
dim(c_DAWBA)

#view(c_DAWBA)
```


##### reverse coding + Means 

SDQ section : making all greater numbers = negative outcomes and lesser numbers 
```{r}
sdq_r = c("s_sdq_1_considerate", "s_sdq_4_shares", "s_sdq_6_solitary", "s_sdq_7_obedient", "s_sdq_9_helpful", "s_sdq_11_good_friend", "s_sdq_14_popular", "s_sdq_17_kind_children", "s_sdq_20_volunteers", "s_sdq_21_reflective", "s_sdq_25_good_attention", "p_sdq_1_considerate", "p_sdq_4_shares", "p_sdq_6_solitary", "p_sdq_7_obedient", "p_sdq_9_helpful", "p_sdq_11_good_friend", "p_sdq_14_popular", "p_sdq_17_kind_children", "p_sdq_20_volunteers", "p_sdq_21_reflective", "p_sdq_25_good_attention")

c_DAWBA[ ,sdq_r] = 2 - c_DAWBA[ ,sdq_r]

#view(c_DAWBA)
```

```{r}
c_DAWBA$MeanSDQ <- rowMeans(c_DAWBA[, 57:122],na.rm=TRUE)
#view(c_DAWBA)
```

Attacthment section :No reverse coding necessary ; higher the number the more attachment
```{r}
c_DAWBA$MeanAttach <- rowMeans(c_DAWBA[, 123:140],na.rm=TRUE)
#view(c_DAWBA)
```

ADHD Section: 
```{r}
c_DAWBA$MeanADHD <- rowMeans(c_DAWBA[, 141:144],na.rm=TRUE)
#view(c_DAWBA)
```

ASD Section:
recoded the social aptitude scale. Higher answers are less likely to match ASD. 
```{r}
asd_r = c("p_asd_soc_apt_scale_1_laugh", "p_asd_soc_apt_scale_2_chat", "p_asd_soc_apt_scale_3_flexible", "p_asd_soc_apt_scale_4_defuse_tense", "p_asd_soc_apt_scale_5_good_loser", "p_asd_soc_apt_scale_6_others_ease", "p_asd_soc_apt_scale_7_tell_others_think_feel", "p_asd_soc_apt_scale_8_apologizes", "p_asd_soc_apt_scale_9_leads",  "p_asd_soc_apt_scale_10_socially_appropriate")

c_DAWBA[ ,asd_r] = 4 - c_DAWBA[ ,asd_r]

```

```{r}
c_DAWBA$MeanASD <- rowMeans(c_DAWBA[, 146:162],na.rm=TRUE)
#view(c_DAWBA)
```

BDD Section: no reverse coding, only did mean
```{r}

R1 <- c_DAWBA[, 163:172] 
R2 <- c_DAWBA[, 174:191]
c_DAWBA$MeanBDD <- rowMeans(cbind(R1, R2),na.rm=TRUE)
#view(c_DAWBA)
```

Conduct Section:  a higher number yields more negative conduct than a lower number.
```{r}
c_DAWBA$MeanCD <- rowMeans(c_DAWBA[, 192:198],na.rm=TRUE)
#view(c_DAWBA)
```

Depression Section:  a higher number yields greater likelihood of depression
```{r}
c_DAWBA$MeanDep <- rowMeans(c_DAWBA[, 199:234],na.rm=TRUE)
#view(c_DAWBA)
```

Eating Section: no reverse coding, only did mean
```{r}

r1 <- c_DAWBA[, 235:239] 
r2 <- c_DAWBA[, 252:270]
c_DAWBA$MeanEat <- rowMeans(cbind(r1, r2),na.rm=TRUE)
#view(c_DAWBA)
```

DMDD Section: no reverse coding, only did mean
```{r}

r_1 <- c_DAWBA[, 271:281] 
r_2 <- c_DAWBA[, 283:299] 
r_3 <- c_DAWBA[, 301:306] 
c_DAWBA$MeanDMDD <- rowMeans(cbind(r_1, r_2, r_3),na.rm=TRUE)
#view(c_DAWBA)
```


Generalized Anxiety Section:  a higher number yields greater liklihood of generalozed anxiety
```{r}
c_DAWBA$MeanGenA <- rowMeans(c_DAWBA[, 307:336],na.rm=TRUE)
#view(c_DAWBA)
```


Mania Section:  a higher number yields greater liklihood of mania/bipolar disorder
```{r}
c_DAWBA$MeanMania <- rowMeans(c_DAWBA[, 337:345],na.rm=TRUE)
#view(c_DAWBA)
```


OCD Section:  a higher number yields greater liklihood of OCD
```{r}
c_DAWBA$MeanOCD<- rowMeans(c_DAWBA[, 346:369],na.rm=TRUE)
#view(c_DAWBA)
```


Panic Section:  
```{r}
c_DAWBA$MeanPanic <- rowMeans(c_DAWBA[, 370:385],na.rm=TRUE)
#view(c_DAWBA)
```


PTSD Section:  a higher number yields greater liklihood of PTSD
```{r}
c_DAWBA$MeanPTSD <- rowMeans(c_DAWBA[, 386:387],na.rm=TRUE)
#view(c_DAWBA)
```


Psychosis Section:  a higher number yields greater liklihood of psychosis
```{r}
c_DAWBA$MeanPsy <- rowMeans(c_DAWBA[, 388:397],na.rm=TRUE)
#view(c_DAWBA)
```


Separation Anxiety Section:  a higher number yields greater liklihood of separation anxiety
```{r}
c_DAWBA$MeanSepA <- rowMeans(c_DAWBA[, 398:419],na.rm=TRUE)
#view(c_DAWBA)
```


Social Phobia Section:  a higher number yields greater liklihood of social phobia
```{r}
c_DAWBA$MeanSoPh <- rowMeans(c_DAWBA[, 420:433],na.rm=TRUE)
#view(c_DAWBA)
```

Specific Phobias Section:  a higher number yields greater specific phobias
```{r}
c_DAWBA$MeanSpPh <- rowMeans(c_DAWBA[, 434:460],na.rm=TRUE)
#view(c_DAWBA)
```

Strengths Section:  a higher number yields greater personal strengths
```{r}
c_DAWBA$MeanStrengths <- rowMeans(c_DAWBA[, 461:503],na.rm=TRUE)
#view(c_DAWBA)
```

Substance Use Section:  a higher number yields greater substance use
```{r}
c_DAWBA$MeanSubst <- rowMeans(c_DAWBA[, 504:514],na.rm=TRUE)
#view(c_DAWBA)
```

Tics Section:  a higher number yields greater presence of tics
```{r}
c_DAWBA$MeanTics <- rowMeans(c_DAWBA[, 515:516],na.rm=TRUE)
#view(c_DAWBA)
```

```{r}
c_DAWBA <- c_DAWBA[, -c(517:531)]
```
Deleting weights+heights
```{r}
c_DAWBA <- c_DAWBA[, -c(240:251)]
```


###### Adding in Means of parents vs children
SDQ
```{r}
sdq_P<- c_DAWBA[, grep("^p_sdq_", names(c_DAWBA))]
sdq_P_Mean <- rowMeans(sdq_P, na.rm=TRUE)

c_DAWBA$sdq_P_Mean <- sdq_P_Mean

sdq_S<- c_DAWBA[, grep("^s_sdq_", names(c_DAWBA))]
sdq_S_Mean <- rowMeans(sdq_S, na.rm=TRUE)

c_DAWBA$sdq_S_Mean <- sdq_S_Mean

#view(c_DAWBA)
```


Attachment
```{r}
att_P<- c_DAWBA[, grep("^p_attachment_", names(c_DAWBA))]
att_P_Mean <- rowMeans(att_P, na.rm=TRUE)

c_DAWBA$att_P_Mean <- att_P_Mean

att_S<- c_DAWBA[, grep("^s_attachment_", names(c_DAWBA))]
att_S_Mean <- rowMeans(att_S, na.rm=TRUE)

c_DAWBA$att_S_Mean <- att_S_Mean
```


ADHD
```{r}
adhd_P<- c_DAWBA[, grep("^p_adhd_", names(c_DAWBA))]
adhd_P_Mean <- rowMeans(adhd_P, na.rm=TRUE)

c_DAWBA$adhd_P_Mean <- adhd_P_Mean

adhd_S<- c_DAWBA[, grep("^s_adhd_", names(c_DAWBA))]
adhd_S_Mean <- rowMeans(adhd_S, na.rm=TRUE)

c_DAWBA$adhd_S_Mean <- adhd_S_Mean
```


BDD
```{r}
bdd_P<- c_DAWBA[, grep("^p_bdd_", names(c_DAWBA))]
bdd_P_Mean <- rowMeans(bdd_P, na.rm=TRUE)

c_DAWBA$bdd_P_Mean <- bdd_P_Mean

bdd_S<- c_DAWBA[, grep("^s_bdd_", names(c_DAWBA))]
bdd_S_Mean <- rowMeans(bdd_S, na.rm=TRUE)

c_DAWBA$bdd_S_Mean <- bdd_S_Mean
```


Depression
```{r}
dep_P<- c_DAWBA[, grep("^p_dep_", names(c_DAWBA))]
dep_P_Mean <- rowMeans(dep_P, na.rm=TRUE)

c_DAWBA$dep_P_Mean <- dep_P_Mean

dep_S<- c_DAWBA[, grep("^s_dep_", names(c_DAWBA))]
dep_S_Mean <- rowMeans(dep_S, na.rm=TRUE)

c_DAWBA$dep_S_Mean <- dep_S_Mean
```


DMDD
```{r}
dmdd_P<- c_DAWBA[, grep("^p_dmdd_", names(c_DAWBA))]
dmdd_P_Mean <- rowMeans(dmdd_P, na.rm=TRUE)

c_DAWBA$dmdd_P_Mean <- dmdd_P_Mean

dmdd_S<- c_DAWBA[, grep("^s_dmdd_", names(c_DAWBA))]
dmdd_S_Mean <- rowMeans(dmdd_S, na.rm=TRUE)

c_DAWBA$dmdd_S_Mean <- dmdd_S_Mean
```


Separation Anxiety
```{r}
sepA_P<- c_DAWBA[, grep("^p_sep_anx", names(c_DAWBA))]
sepA_P_Mean <- rowMeans(sepA_P, na.rm=TRUE)

c_DAWBA$sepA_P_Mean <- sepA_P_Mean

sepA_S<- c_DAWBA[, grep("^s_sep_anx", names(c_DAWBA))]
sepA_S_Mean <- rowMeans(sepA_S, na.rm=TRUE)

c_DAWBA$sepA_S_Mean <- sepA_S_Mean
```


Social Phobia
```{r}
socP_P<- c_DAWBA[, grep("^p_social_", names(c_DAWBA))]
socP_P_Mean <- rowMeans(socP_P, na.rm=TRUE)

c_DAWBA$socP_P_Mean <- socP_P_Mean

socP_S<- c_DAWBA[, grep("^s_social_", names(c_DAWBA))]
socP_S_Mean <- rowMeans(socP_S, na.rm=TRUE)

c_DAWBA$socP_S_Mean <- socP_S_Mean
```


Specific Phobia
```{r}
speP_P<- c_DAWBA[, grep("^p_specific_", names(c_DAWBA))]
speP_P_Mean <- rowMeans(speP_P, na.rm=TRUE)

c_DAWBA$speP_P_Mean <- speP_P_Mean

speP_S<- c_DAWBA[, grep("^s_specific_", names(c_DAWBA))]
speP_S_Mean <- rowMeans(speP_S, na.rm=TRUE)

c_DAWBA$speP_S_Mean <- speP_S_Mean
```


Positive Attributes (strengths)
```{r}
str_P<- c_DAWBA[, grep("^p_positive_", names(c_DAWBA))]
str_P_Mean <- rowMeans(str_P, na.rm=TRUE)

c_DAWBA$str_P_Mean <- str_P_Mean

str_S<- c_DAWBA[, grep("^s_positive_", names(c_DAWBA))]
str_S_Mean <- rowMeans(str_S, na.rm=TRUE)

c_DAWBA$str_S_Mean <- str_S_Mean
```


General Anxiety Disorder
```{r}
gad_P<- c_DAWBA[, grep("^p_gad_", names(c_DAWBA))]
gad_P_Mean <- rowMeans(gad_P, na.rm=TRUE)

c_DAWBA$GenA_P_Mean <- gad_P_Mean

gad_S<- c_DAWBA[, grep("^s_gad_", names(c_DAWBA))]
gad_S_Mean <- rowMeans(gad_S, na.rm=TRUE)

c_DAWBA$GenA_S_Mean <- gad_S_Mean
```


OCD
```{r}
ocd_P<- c_DAWBA[, grep("^p_ocd_", names(c_DAWBA))]
ocd_P_Mean <- rowMeans(ocd_P, na.rm=TRUE)

c_DAWBA$ocd_P_Mean <- ocd_P_Mean

ocd_S<- c_DAWBA[, grep("^s_ocd_", names(c_DAWBA))]
ocd_S_Mean <- rowMeans(ocd_S, na.rm=TRUE)

c_DAWBA$ocd_S_Mean <- ocd_S_Mean
```


ODD
```{r}
odd_P<- c_DAWBA[, grep("^p_odd_", names(c_DAWBA))]
odd_P_Mean <- rowMeans(odd_P, na.rm=TRUE)

c_DAWBA$odd_P_Mean <- odd_P_Mean

odd_S<- c_DAWBA[, grep("^s_odd_", names(c_DAWBA))]
odd_S_Mean <- rowMeans(odd_S, na.rm=TRUE)

c_DAWBA$odd_S_Mean <- odd_S_Mean
```


Panic
```{r}
pan_P<- c_DAWBA[, grep("^p_panic_", names(c_DAWBA))]
pan_P_Mean <- rowMeans(pan_P, na.rm=TRUE)

c_DAWBA$pan_P_Mean <- pan_P_Mean

pan_S<- c_DAWBA[, grep("^s_panic_", names(c_DAWBA))]
pan_S_Mean <- rowMeans(pan_S, na.rm=TRUE)

c_DAWBA$pan_S_Mean <- pan_S_Mean
```


PTSD
```{r}
ptsd_P<- c_DAWBA[, grep("^p_ptsd_", names(c_DAWBA))]
ptsd_P_Mean <- rowMeans(ptsd_P, na.rm=TRUE)

c_DAWBA$ptsd_P_Mean <- ptsd_P_Mean

ptsd_S<- c_DAWBA[, grep("^s_ptsd_", names(c_DAWBA))]
ptsd_S_Mean <- rowMeans(ptsd_S, na.rm=TRUE)

c_DAWBA$ptsd_S_Mean <- ptsd_S_Mean
```

```{r}
view(c_DAWBA)
```

```{r}
c_DAWBA$Participant <- 1:nrow(c_DAWBA)
```




###### Looking at the percentage of questions where the child rated themselves higher based off section means. 

Depression
```{r}
count_Sdep_greater<- sum(c_DAWBA$dep_S_Mean > c_DAWBA$dep_P_Mean, na.rm=TRUE)
(count_Sdep_greater/(nrow(c_DAWBA)))*100
```

Generalized Anxiety
```{r}
count_Sga_greater<- sum(c_DAWBA$GenA_S_Mean > c_DAWBA$GenA_P_Mean, na.rm=TRUE)
(count_Sga_greater/(nrow(c_DAWBA)))*100
```

SDQ
```{r}
count_Sdq_greater<- sum(c_DAWBA$sdq_S_Mean > c_DAWBA$sdq_P_Mean, na.rm=TRUE)
(count_Sdq_greater/(nrow(c_DAWBA)))*100
```

Attachment
```{r}
count_Satt_greater<- sum(c_DAWBA$att_S_Mean > c_DAWBA$att_P_Mean, na.rm=TRUE)
(count_Satt_greater/(nrow(c_DAWBA)))*100
```

ADHD
```{r}
count_Sadhd_greater<- sum(c_DAWBA$adhd_S_Mean > c_DAWBA$adhd_P_Mean, na.rm=TRUE)
(count_Sadhd_greater/(nrow(c_DAWBA)))*100
```

BDD
```{r}
count_Sbdd_greater<- sum(c_DAWBA$bdd_S_Mean > c_DAWBA$bdd_P_Mean, na.rm=TRUE)
(count_Sbdd_greater/(nrow(c_DAWBA)))*100
```

DMDD
```{r}
count_Sdmdd_greater<- sum(c_DAWBA$dmdd_S_Mean > c_DAWBA$dmdd_P_Mean, na.rm=TRUE)
(count_Sdmdd_greater/(nrow(c_DAWBA)))*100
```

Separation Anxiety
```{r}
count_SepA_greater<- sum(c_DAWBA$sepA_S_Mean > c_DAWBA$sepA_P_Mean, na.rm=TRUE)
(count_SepA_greater/(nrow(c_DAWBA)))*100
```

Social Phobias
```{r}
count_SocP_greater<- sum(c_DAWBA$socP_S_Mean > c_DAWBA$socP_P_Mean, na.rm=TRUE)
(count_SocP_greater/(nrow(c_DAWBA)))*100
```

Specific Phobias
```{r}
count_SpeP_greater<- sum(c_DAWBA$speP_S_Mean > c_DAWBA$speP_P_Mean, na.rm=TRUE)
(count_SpeP_greater/(nrow(c_DAWBA)))*100
```

OCD
```{r}
count_Socd_greater<- sum(c_DAWBA$ocd_S_Mean > c_DAWBA$ocd_P_Mean, na.rm=TRUE)
(count_Socd_greater/(nrow(c_DAWBA)))*100
```

ODD
```{r}
count_Sodd_greater<- sum(c_DAWBA$odd_S_Mean > c_DAWBA$odd_P_Mean, na.rm=TRUE)
(count_Sodd_greater/(nrow(c_DAWBA)))*100
```

Panic
```{r}
count_Span_greater<- sum(c_DAWBA$pan_S_Mean > c_DAWBA$pan_P_Mean, na.rm=TRUE)
(count_Span_greater/(nrow(c_DAWBA)))*100
```

PTSD
```{r}
count_Sptsd_greater<- sum(c_DAWBA$ptsd_S_Mean > c_DAWBA$ptsd_P_Mean, na.rm=TRUE)
(count_Sptsd_greater/(nrow(c_DAWBA)))*100
```

Positive 
```{r}
count_Spos_greater<- sum(c_DAWBA$str_S_Mean > c_DAWBA$str_P_Mean, na.rm=TRUE)
(count_Spos_greater/(nrow(c_DAWBA)))*100
```

```{r}
b<-(3/14)*100
100-b

```







